---
title: "A plot with Plotly"
author: "K. van Splunter"
date: "23 March 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Introduction

The assignment is to show a plot made with Ploty in a presentation created with R Markdown

## Some Notes

To create a plot with Plotly, the package must be loaded.

`library(plotly)`

## Data

- Uses data from **CBS** (Centraal Bureau voor de Statistiek)
    - A Dutch government agency that collects and processes all kinds of data
    - Take a look at the [website](https://www.cbs.nl/en-gb)
  
## Info

- Data is about several types of registered crime in the Netherlands for the period 2010-2016
    - per 1,000 inhabitants
```{r load_data, comment =""}
data <- read.csv("criminaliteit.csv", sep = ";", skip=4, dec = ",")
data <- data[-57,]
data$Perioden <- as.factor(data$Perioden)
names(data) <- c("TypeOfCrime", "Year", "Crimeper1000Inhabitants")
data$TypeOfCrime <- factor(data$TypeOfCrime, labels = c("Property crime", "Destruction",
                                                        "Violent crime",
                                                        "Other crimes in criminal law",
                                                        "Traffic related crime",
                                                        "Drugs related crime",
                                                        "Weapon related crime", "Other crime"))
```

## Plot

```{r plot, fig.align='center'}
plott <- plot_ly(data, x = ~Year, y = ~Crimeper1000Inhabitants, color = ~TypeOfCrime,
                 legendgroup = ~TypeOfCrime) %>%
    add_lines() %>%
    layout(title = "Amount of crime per 1,000 inhabitants in the Netherlands for the period 2010-2016", yaxis = list(title = "Amount of crime per 1,000 inhabitants"))
plott
```